Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-19 2015-turklang-kazdep/paper.tex
more abs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60845 72bbbca6-d526-0410-a7d9-f06f51895060

%250-300-word ``extended abstract in English''
\abstract{
This article describes the first steps towards a free/open-source dependency treebank
for Kazakh based on universal dependency (UD) annotation standards. The treebank is 
based on texts from a range of open-source and public domain sources ensuring its 
free availability and extensibility. 
}

>>>>

%250-300-word ``extended abstract in English''
\abstract{
This article describes the first steps towards a free/open-source dependency treebank
for Kazakh based on universal dependency (UD) annotation standards. The treebank contains
302 sentences and is based on texts from a range of open-source and public domain sources.
This ensures its free availability and extensibility. Texts in the treebank are first morphologically 
analysed and disambiguated and then annotated manually for dependency structure. 
}
